Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
pass on results

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines.  We
analyzed the impact of two orthogonal dimensions in this study: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing these inputs.

@@

\section{Discussion}

It is important to highlight that our treatment on both dimensions of
analysis--test mining and fuzzing--could be improved by selecting more
test cases or using more advanced fuzzing tools. The main rationale is
that if these techinques perform well with the objects we used
(Section~\ref{sec:methodology}) then the approach would perform even
better with more elaborate objects.

\Fix{...}

>>>>

The overarching goal of our study is to identify the ability of simple
techniques to find bugs in \js\ engines with cross-engine differential
testing.  We analyzed the impact of two orthogonal dimensions in this
study: test mining and fuzzing. The first dimension focuses on the
impact of inputs, mined from the web, in bug finding whereas the
second dimension focuses on the impact of fuzzing these inputs.

@@
